### 2022-10-20 types.tex
removing fold/unfold points to a need to treat ingress/egress differently. This in turn makes the overall type system duplicate a bunch of rules but also make more sense.
If we want to just have one, it looks like "just have egress" is the one that hangs together the most right now.

    {\inferrule{A : in(dₐ), A : out(dₐ),… ;A : τₐ,…;.  ⊢ p : τ}
      {⊢ "declare"~A…~"in"~p : τ}}

    {
      \inferrule{\inputs(\op) = τ \\ 
        C;Γ;. ⊢ p : τ \\ C';Γ';d.p.\op[0] ⊢ p' : τ'}
                {{C,C'};Γ,Γ';{d} ⊢ [p]\op[p'] : τ'}}

    {\inferrule[relevant-parallel]
      {C₁;Γ_1;d[n] ⊢ p₁ : τ₁ \\ C₂;Γ_2;d[n+1] ⊢ p₂ : τ₂}
      {C₁,C₂;Γ_1,Γ_2;d[n] ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[general-parallel]
      {C₁;Γ_1;. ⊢ p₁ : τ₁ \\ C₂;Γ_2;. ⊢ p₂ : τ₂}
      {C₁,C₂;Γ_1,Γ_2; . ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[exchange-C]
      {C,C_2,C_1,C' ;Γ; d ⊢ p : τ}
      {C,C_1,C_2,C' ;Γ; d ⊢ p : τ}}

    {\inferrule[exchange-gamma]
      {C ;Γ,Γ_1,Γ_2,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_2,Γ_1,Γ'; d ⊢ p : τ}}

    {\inferrule[weaken-gamma]
      {C ;Γ,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_w,Γ'; d ⊢ p : τ}}

    {\inferrule[contract-gamma]
      {C ;Γ,Γ_c,Γ_c,Γ' ; d ⊢ p : τ}
      {C ;Γ,Γ_c,Γ'; d ⊢ p : τ}}

    {\inferrule[unfold]{A:d',C;Γ;d[A/d] ⊢ p : τ}{A:d',C;Γ;d ⊢ p : τ}}

    {\inferrule[fold]{A:d',C;Γ;d⊢ p : τ}{A:d',C;Γ;d[A/d]⊢ p : τ}}

    {\inferrule[varref-out]{Γ ⊢ d : τ}{A:out(d);Γ;d ⊢ A : τ}}

    {\inferrule[varref-in]{}{A:in(d);A : τ; . ⊢ A : τ}}

    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ C;Γ;d' ⊢ p : τ}{C;Γ;d ⊢ p : τ}}

@@

\end{mathpar}    
    \caption{Types: derivations }
    \label{fig:types2}
\end{figure}
\begin{figure}
\begin{mathpar}

@@

@@

>>>>

    {\inferrule{A : in(dₐ), A : out(dₐ),… ;A : τₐ,…  ⊢ p}
      {⊢ "declare"~A…~"in"~p}}

    {
      \inferrule[pivot]{\inputs(\op) = τ \\ 
        C;Γ ⊢ p : d~τ \\ C';Γ';d.op[0] ⊢ p'}
                {{C,C'};Γ,Γ' ⊢ [p]\op[p']}}

    {
      \inferrule[inward]{\inputs(\op) = τ \\ 
        C;Γ ⊢ p : d~τ}
                {{C};Γ,Γ' ⊢ [p]\op : d.\op~τ'}}

{
      \inferrule[outward]{Γ ⊢ d : τ \\ \inputs(\op) = τ \\
        C;Γ;d.\op[0] ⊢ p'}
                {{C};Γ;d ⊢ \op[p']}}

    {\inferrule[out-parallel]
      {C₁;Γ_1;d[n] ⊢ p₁ \\ C₂;Γ_2;d[n+1] ⊢ p₂}
      {C₁,C₂;Γ_1,Γ_2;d[n] ⊢ (p₁ ∣ p₂)}}

    {\inferrule[in-parallel]
      {C₁;Γ_1 ⊢ p₁ : d₁~τ₁ \\ C₂;Γ_2 ⊢ p₂ : d₂~τ₂}
      {C₁,C₂;Γ_1,Γ_2 ⊢ (p₁ ∣ p₂) : (d₁ ∣ d₂)~(τ₁ ∣ τ₂)}}

%    {\inferrule[unfold]{A:d',C;Γ;d[A/d] ⊢ p : τ}{A:d',C;Γ;d ⊢ p : τ}}

%    {\inferrule[fold]{A:d',C;Γ;d⊢ p : τ}{A:d',C;Γ;d[A/d]⊢ p : τ}}

    {\inferrule[varref-out]{Γ ⊢ d : τ}{A:out(d);Γ;d ⊢ A}}

    {\inferrule[varref-in]{}{A:in(d);A : τ ⊢ A : d~τ}}

    {\inferrule[axoim-transform-in]{Γ ⊢ d ⇝ d' \\ C;Γ ⊢ p : d~τ}{C;Γ ⊢ p : d'~τ}}

    {\inferrule[axoim-transform-out]{Γ ⊢ d ⇝ d' \\ C;Γ;d' ⊢ p}{C;Γ;d ⊢ p}}

@@

\end{mathpar}    
    \caption{Types: derivations }
    \label{fig:types2}
\end{figure}

@@

    {\inferrule[exchange-C-in]
      {C,C_2,C_1,C' ;Γ ⊢ p : d~τ}
      {C,C_1,C_2,C' ;Γ ⊢ p : d~τ}}

    {\inferrule[exchange-gamma-in]
      {C ;Γ,Γ_1,Γ_2,Γ' ⊢ p : d~τ}
      {C ;Γ,Γ_2,Γ_1,Γ' ⊢ p : d~τ}}

    {\inferrule[weaken-gamma-in]
      {C ;Γ,Γ'  ⊢ p : d~τ}
      {C ;Γ,Γ_w,Γ' ⊢ p : d~τ}}

    {\inferrule[contract-gamma-in]
      {C ;Γ,Γ_c,Γ_c,Γ' ⊢ p : d~τ}
      {C ;Γ,Γ_c,Γ' ⊢ p : d~τ}}

    {\inferrule[exchange-C-out]
      {C,C_2,C_1,C' ;Γ; d ⊢ p}
      {C,C_1,C_2,C' ;Γ; d ⊢ p}}

    {\inferrule[exchange-gamma-out]
      {C ;Γ,Γ_1,Γ_2,Γ'; d ⊢ p}
      {C ;Γ,Γ_2,Γ_1,Γ'; d ⊢ p}}

    {\inferrule[weaken-gamma-out]
      {C ;Γ,Γ'; d  ⊢ p}
      {C ;Γ,Γ_w,Γ'; d ⊢ p}}

    {\inferrule[contract-gamma-out]
      {C ;Γ,Γ_c,Γ_c,Γ'; d ⊢ p}
      {C ;Γ,Γ_c,Γ'; d ⊢ p}}

\end{mathpar}    
    \caption{Types: boring structural stuff }
    \label{fig:types-structural}
\end{figure}

@@

Another note: the "natural" way to do derivations might change between a push-oriented and a pull-oriented worldview---worth thinking about / playing around with.

On the above: turns out I did stay up and push it through and... it seems to work! Shockingly! Quite Interesting.
